Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England: Supplementary materials

### 2021-09-09 analysis/report/draft-supplement.Rmd
fix path

```{r seconddose_postest, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
plot_seconddose_all <- read_rds(here("output", "descriptive", "secondose", "plot_seconddose_all.rds"))
plot_seconddose_all
```

>>>>

```{r seconddose_postest, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
plot_seconddose_all <- read_rds(here("output", "descriptive", "seconddose", "plot_seconddose_all.rds"))
plot_seconddose_all
```
